Paper Six Summary

### 2015-10-27 hw/read/6/summary.tex
Added hypothesis
Added informative visualizations

\section*{Feature Extraction}
\begin{description}
\item[{Motivational Statements}]  While within-project defect prediction can be very effective, new projects don't have the volume of data needed to create these models. Cross-project defect prediction models aim to help with this issue, but so far the results have largely been disappointing. The authors hope to show that cross-project defect prediction can be roughly as effective as traditional defect prediction by using a different set of measures, namely those based on a variety of tradeoffs of time-and-cost vs. quality.
\item[{Statistical tests}] The authors used the area under the ROC curve (AUC), AUCCE, precision, recall, and f-measure statistical tests to report their results. They varied the cutoffs for precision, recall, and f-measure but used the standard 0.5 cutoff for their sanity checks.

>>>>

\section*{Feature Extraction}
\begin{description}
\item[{Motivational Statements}]  While within-project defect prediction can be very effective, new projects don't have the volume of data needed to create these models. Cross-project defect prediction models aim to help with this issue, but so far the results have largely been disappointing. The authors hope to show that cross-project defect prediction can be roughly as effective as traditional defect prediction by using a different set of measures, namely those based on a variety of tradeoffs of time-and-cost vs. quality.
\item[{Hypothesis}] The hypothesis of this paper is that performance of cross-project defect prediction models is similar to the performance of within-project defect prediction when assessing performance within reasonable and practical resource limitations.
\item[{Statistical tests}] The authors used the area under the ROC curve (AUC), AUCCE, precision, recall, and f-measure statistical tests to report their results. They varied the cutoffs for precision, recall, and f-measure but used the standard 0.5 cutoff for their sanity checks.
\item[{Informative Visualization}] Figure 2 gives an informative comparison of cross and within-project model performance assessed by multiple performance metrics. It visualizes how well the distribution of results overlap for within and cross-project model performance even though within-project generally has higher performance. The addition of p-values shows how the differences lack significance. Figure 4 is also very informative, showing how weighting the defects by density affects AUC. Both cross-project and within-project have similar results and the addition of random and optimal baselines are useful for comparison.
